Student Log-Data from a Randomized Evaluation of Educational Technology: A Causal Case Study

### 2020-02-10 paper.Rnw
added lines to mediation table, modified caption of tab 2

print(xtable(matchTEtab,
  align='rrllccc',
  caption='Estimates and sensitivity analysis of the effect of hint usage.',
  label='tab:matchResults'),
  include.rownames=FALSE,sanitize.text.function =function(x) x,add.to.row=addtorow,include.colnames=FALSE)
@

@@

\begin{table}
\begin{tabular}{llll}
Effect&Method&Estimate&CI\\
<<mediationTable,echo=FALSE>>=
cat(
  '$1-p_0=\\EE[H(1)-H(0)|Z=1]$ & By Definition&',round(mixProp,2),'&n/a\\\\
$TOT=\\EE[Y(Z=1,H=1)-Y(Z=1,H=0)|Z=1]$&Matching&',round(effects[['tot_eff']][['coefficients']],2),'&',printci(with(effects[['tot_eff']],c(conf.low,conf.high))),'\\\\
$\\Delta=\\EE[Y(1,H(1))-Y(1,H(0))|Z=1]$&$(1-p_0)TOT$&',round(mixProp*effects[['tot_eff']][['coefficients']],2),'&',printci(mixProp*with(effects[['tot_eff']],c(conf.low,conf.high))),'\\\\
$\\Xi=\\EE[Y(1,H(0))-Y(0,H(0))]$&Regression \\eqref{eq:directEffReg}&',round(dir1.1t[1],2),'&',printci(dir1.1ci),'\\\\
$\\Xi=\\EE[Y(1,H(0))-Y(0,H(0))]$& \\eqref{eq:directEffReg} + covariates&',round(dir2.1t[1],2),'&',printci(dir2.1ci),'\n')
@
\end{tabular}
\caption{Estimated effects in mediation analysis. }
\label{tab:mediation}
\end{table}

>>>>

print(xtable(matchTEtab,
  align='rrllccc',
  caption='Estimates, standard errors, and sensitivity analysis of the weighted average effect of hint usage, under different weighting schemes.',
  label='tab:matchResults'),
  include.rownames=FALSE,sanitize.text.function =function(x) x,add.to.row=addtorow,include.colnames=FALSE)
@

@@

\begin{table}
\begin{tabular}{llll}
\hline
Effect&Method&Estimate&CI\\
\hline
<<mediationTable,echo=FALSE>>=
cat(
  '$1-p_0=\\EE[H(1)-H(0)|Z=1]$ & By Definition&',round(mixProp,2),'&n/a\\\\
$TOT=\\EE[Y(Z=1,H=1)-Y(Z=1,H=0)|Z=1]$&Matching&',round(effects[['tot_eff']][['coefficients']],2),'&',printci(with(effects[['tot_eff']],c(conf.low,conf.high))),'\\\\
$\\Delta=\\EE[Y(1,H(1))-Y(1,H(0))|Z=1]$&$(1-p_0)TOT$&',round(mixProp*effects[['tot_eff']][['coefficients']],2),'&',printci(mixProp*with(effects[['tot_eff']],c(conf.low,conf.high))),'\\\\
$\\Xi=\\EE[Y(1,H(0))-Y(0,H(0))]$&Regression \\eqref{eq:directEffReg}&',round(dir1.1t[1],2),'&',printci(dir1.1ci),'\\\\
$\\Xi=\\EE[Y(1,H(0))-Y(0,H(0))]$& \\eqref{eq:directEffReg} + covariates&',round(dir2.1t[1],2),'&',printci(dir2.1ci),'\\\\\n')
@
\hline
\end{tabular}
\caption{Estimated effects in mediation analysis. }
\label{tab:mediation}
\end{table}

### 2020-02-10 paper.tex
added lines to mediation table, modified caption of tab 2

\begin{table}
\begin{tabular}{llll}
Effect&Method&Estimate&CI\\
$1-p_0=\EE[H(1)-H(0)|Z=1]$ & By Definition& 0.3 &n/a\\
$TOT=\EE[Y(Z=1,H=1)-Y(Z=1,H=0)|Z=1]$&Matching& -0.14 & [-0.25,-0.03] \\
$\Delta=\EE[Y(1,H(1))-Y(1,H(0))|Z=1]$&$(1-p_0)TOT$& -0.04 & [-0.07,-0.01] \\
$\Xi=\EE[Y(1,H(0))-Y(0,H(0))]$&Regression \eqref{eq:directEffReg}& 0.14 & [-0.08,0.37] \\
$\Xi=\EE[Y(1,H(0))-Y(0,H(0))]$& \eqref{eq:directEffReg} + covariates& 0.18 & [-0.01,0.38]

\end{tabular}
\caption{Estimated effects in mediation analysis. }
\label{tab:mediation}
\end{table}

>>>>

Table \ref{tab:mediation} summarizes our mediation results.

\begin{table}
\begin{tabular}{llll}
\hline
Effect&Method&Estimate&CI\\
\hline
$1-p_0=\EE[H(1)-H(0)|Z=1]$ & By Definition& 0.3 &n/a\\
$TOT=\EE[Y(Z=1,H=1)-Y(Z=1,H=0)|Z=1]$&Matching& -0.14 & [-0.25,-0.03] \\
$\Delta=\EE[Y(1,H(1))-Y(1,H(0))|Z=1]$&$(1-p_0)TOT$& -0.04 & [-0.07,-0.01] \\
$\Xi=\EE[Y(1,H(0))-Y(0,H(0))]$&Regression \eqref{eq:directEffReg}& 0.14 & [-0.08,0.37] \\
$\Xi=\EE[Y(1,H(0))-Y(0,H(0))]$& \eqref{eq:directEffReg} + covariates& 0.18 & [-0.01,0.38] \\

\hline
\end{tabular}
\caption{Estimated effects in mediation analysis. }
\label{tab:mediation}
\end{table}
